Non-target amplification

### 2022-03-23 07--nontarget_amplification.Rmd
working on reviewer request

>>>>

## Look for overlap in oomycetes detected

A reviewer requested that we look to see if any oomycetes are detected by ITS1 that are not detected by rps10.

```{r}
obj <- parse_tax_data(abundance_asv, class_cols = 'taxonomy', class_sep = ';',
                      class_regex = '^(.+)--(.+)--(.+)$',
                      class_key = c(taxon = 'taxon_name', boot = 'info', rank = 'taxon_rank'))
obj$data$class_data <- NULL

# Just look at oomycetes
obj <- filter_taxa(obj, taxon_names == "Oomycetes", supertaxa = FALSE, subtaxa = TRUE)

# Just look at species data
obj <- filter_taxa(obj, taxon_ranks == "Species", supertaxa = FALSE)

# Sum data by taxon
obj$data$tax_abund <- calc_taxon_abund(obj, data = "tax_data", cols = metadata$sample_id, groups = metadata$locus)

# Color by locus
obj$data$tax_abund$locus <- "Both"
obj$data$tax_abund$locus[obj$data$tax_abund$rps10 >= minimum_read_count & obj$data$tax_abund$ITS < minimum_read_count] <- 'Rps10'
obj$data$tax_abund$locus[obj$data$tax_abund$rps10 < minimum_read_count & obj$data$tax_abund$ITS >= minimum_read_count] <- 'ITS1'
table(obj$data$tax_abund$locus)

# Plot
obj %>%
  heat_tree(node_label = taxon_names,
            node_size = n_obs)

```
